Notebook of learning from ensemble labels

### 2021-08-09 docs/notebook_learn_dl_ensemble.Rmd
Weighted loss seems to have an issue, not a big deal though

```
python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

>>>>

```
python hrlcm/fit_compose_lr.py --exp_name unet_no_weight_epoch400 --num_workers 32 --gpu_devices '0,1,2,3'
```

@@

```
python hrlcm/predict.py --args_path 'results/dl/unet_no_weight_epoch400/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_no_weight_epoch400/checkpoints/interim.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
```
